---
title: "W_UP_01"
author: "William Patrick Oliver"
date: "Summer 2022"
output: html_document
---



The report structure should include five sections.  see below



```{r include=FALSE,echo=FALSE}
require(tigerstats)
require(tidyverse)
mydata <- read.csv(file="pushups.csv")
```

# Introduction

<!--In this section you explain what you are trying to show. Where did the data come from? What is the research or other question you are trying to answer?!-->

Create an Rstudio project in your shared space on rstudio.cloud.  Using the dataset called pushups from the tigerstats package in R; answer the question posed by this null and alternate hypothesis in an html markdown document.

$H_0$: There is no difference between the average number of pushups of line vs skill players

$H_A$: The average number of pushups done by line players is statistically different than that of skill players.

# Methods

<!--Decide on your methods: use "variable analysis" or other appropriate descriptors. Make sure to choose at least one graphical method and at least one numerical method.!-->

Positions are a Categorical variable. pushups is a numerical variable. I will do an analysis that explains push-ups based on position



# Results

<!--Divide this section into two sub-sections: One for your descriptive results and one for your inferential results.!-->

## Descriptive Results

### Graphical Descriptive Results


<!--Graphical results here. Make sure to show your code. Provide appropriate labels for axes, giving units if possible, and provide a good title for the graph, too. Use the graphical results to describe the patterns if any that exist in the data as focused toward the research question!-->
```{r}
boxplot(pushups~position,data=mydata)
```


A table displaying the proportion of how many pushups people from the line and people from the skill can do. with pushups to gauge the Y-axis and the line and skill on the X it shows that those in line have a smaller push-up rate than those belonging to skill.


### Numerical Descriptive Results

<!--Numerical results go here. Use the numerical results to describe the patterns if any that exist in the data as focused toward the research question!-->
```{r}
favstats(pushups~position,data=mydata)
```


A chart depicting the Mean,Median and Mode of those who do line position and those that do Skill. showing that again those who do things by skill are more successful than those in line.


## Inferential Results

<!--State hypothesis clearly. Make sure your discussion of the inferential test covers all the aspects that the test output produces, such as test statistic, p-value etc. Make a decision about the null hypothesis, explain the assumptions on which the selected test/procedure was based, and why the chosen procedure satisfys the assumptions and is appropriate to answer the research question!-->
```{r}
t.test(pushups~position,data=mydata)
```
This shows that our p-val. is .000009421, our t is in the negative with -5.4341, and our df is 27.079. with the alt. hypothesis being true difference in means between group line and skill is not equal to 0. if the value is greater than .05 you fail the hypothesis. since the p-val. is small so we reject the null hypothesis. I'm a solid 95% sure that skill does more push-ups than Line. and if i'm wrong I'll eat my Flex tape.


# Discussion and Conclusion

<!--Discussion and conclusion here. If you found a relationship be sure to consider whether the relationship occurs because one of the variavbles causes the other, or whether they perhasps are related for some other reason. Watch the chapter 6 videos from the GeorgeTown videos collection.!-->

The original question was this: 'Who could do the most push-ups?' the SKILL position or the LINE position under a specific amount of time? our response: based off our numerical descriptive results & our inferential result; The SKILL position can do MORE push-ups than the LINE position under any amount of time given. using a T-test we found out the the maximum probabbility of the line and skill doing push-ups had betrayed and failed the hypothesis making it near impossible for line to do more push-ups than the Skill. we had used a boxplot & a table to figure out our values and percentages. The Median & average were much higher for the SKILL position than the LINE position.